\section{Facilities}
\begin{labeling}
    \item [\underline{Mine}:] Lots of Uranium deposits in Australia, Iran, US, Canada, Russia,
        Africa, Some in China, Almost none in India.
    \item [\underline{Milling}:] Typically co-located with Mine, like with gold and other
        metal  extraction. Produces yellowcake.
    \item [\underline{Conversion}:] Chemical process to obtain UF$_6$ gas.
    \item [\underline{Enrichment}:] Increases the percentage of fissile species in order to
        make fuel.
        \begin{labeling}
            \item [\underline{Low Enriched U}:] $<20\%$ \U235, statutory limit of $<5\%$
            \item [\underline{Mid Enriched U}:] $20 - 80\%$ \U235
            \item [\underline{Highly Enriched U}:] $80+\%$ \U235, Typically at 95-99\% is
                weapons grade.
        \end{labeling}
        Mass differences are small, $\Delta = M_{^{238}U} - M_{^{235}U} \approx 3 \mathrm{am} = 5\times 10^{-27} \mathrm{kg}$.
        Types of enrichment:
        \begin{labeling}
            \item [\underline{Electromagnetic}:] Mass spec, Calutron, Expensive, Manhattan project, Iraq.
                % FIXME Image of calutron
            \item [\underline{Diffussion}:] Perforated holes, pressure differential, Many stages - 100s to 1000s.
                % FIXME Image of perforated holes
            \item [\underline{Centrifuges}:] Fewer stages
                % FIXME Image of centrifuge
            \item [\underline{Laser}:] Not industrial scale yet, light finds resonance in nucleus.
                % FIXME Image of beam hitting stream
        \end{labeling}
    \item [\underline{Fuel Fab}:] Creates fuel rods with cladding. Different procedures for different Rx types
        and fuel types.
    \item [\underline{Front End}:] All of the above facilities taken together are called the Front End.
    \item [\underline{Rx}:] Many different kinds of reactors. What the rest of this course is about.
    \item [\underline{On-site Storage}:] Cooling ponds, dry storage.
    \item [\underline{Interim Storage}:] Off-site, centralized, medium term dry storage.
    \item [\underline{Deep Geologic Repositories}:] Meant to secure long-lived species for 10,000 - 1 million years.
        \begin{labeling}
            \item [\underline{Yucca Mountain}:] Above Water Table
            \item [\underline{WIPP}:] Salt-based
            \item [\underline{Volcanic}:] Earth sealing
            \item [\underline{Deep Borehole}:] Relies on oil industry technology
        \end{labeling}
        Tradeoffs and concerns are recoverable vs non-recoverable, wasteform, rock specific heat, packing density.
    \item [\underline{Reprocessing} or \underline{Separations}:] Essential for closed fuel cycles. Most separate
        chemically. Laser separation promises nuclide specific separations. The following element groups are
        commonly seapared together:
        \begin{labeling}
            \item [\underline{Actinides}:] Anything in the Ac row.
            \item [\underline{Transuranics (TRU)}:] Anything with $Z > 92$.
            \item [\underline{Minor Actinides}:] TRU w/out Pu
            \item [\underline{Fission Products}:] Fission fragments produced in the reactor.
        \end{labeling}
        Various processes include:
        \begin{itemize}
            \item UREX is a reprocessing method that produces uranium in the product and sends everything
                else to waste.
            \item PUREX and PUREX+ keep urnaium and plutonium and send everything else to waste.
            \item Sometimes will partition Cs and Sr to send \Cs137 and \Sr90 to low-level waste. These are
                major early heat load otherwise.
        \end{itemize}
    \item [\underline{Backend}:] Storage, reprocessing and sometimes fuel fab are collectively called the backend.
\end{labeling}

Except for the reactor, and ignoring radioactive decay, all fuel cycle facilities must obey conservation of mass.

\underline{HW for Next Class}: bring basic design information about a reactor type ready to share. Slides OK. Find info
about geometry, chemical form, number of assemblies, fuel cycle, etc.
Assign: BWR, PWR, Candu, SMR, Thorium, HTGR, Candle, Gas-Cooled, Fast Burner, Fast Breeder, Chicago Pile, HFIR, ATR,
RBMK, UNGG, Traveling Wave, PebbleBed, 4S, VVER, RAPID-C, Molten Salt, Accellerator-driven sub-critical, MYRRHA.
